---
title: "Penguin"
format: html
editor: source
---

## Introduction

This document offers a straightforward analysis of the well-known penguin dataset. It is designed to complement the [Productive R Workflow](https://www.productive-r-workflow.com) online course.

You can read more about the penguin dataset [here](https://allisonhorst.github.io/palmerpenguins/).

Let's load libraries before we start!

```{r, message=F, warning=F}
# load the tidyverse
library(tidyverse)
```


## Loading data

The dataset has already been loaded and cleaned in the previous step of this pipeline.

Let's load the clean version, together with a few functions available in `functions.R`.

```{r}
# Source functions
source(file="functions.R")

# Read the clean dataset
data <- readRDS(file = "../input/clean_data.rds")
```


## Bill length

Now, let's make some descriptive analysis about the bill length, including summary statistics and graphs:

```{r}
# Summary
summary(data)

# Calculating mean bill length for different species and islands using dplyr
data %>%
  filter(species == "Adelie") %>%
  group_by(island) %>%
  summarize(mean_bill_length = round(mean(bill_length_mm, na.rm = TRUE), 2))

# Use the function in functions.R
create_scatterplot(data, "Adelie", "Torgersen")

```


